\bf On semidefinite-representable sets over valuation fields

### 2025-05-19 article/paper_padic_spec.tex
commit by Simone
section LP

\begin{algorithm}
    \caption{\textbf{SOLVELPval}($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
        \RETURN [INFEAS, []] \label{step:linear_empty}
      \ENDIF
      \IF{$D \neq {\bf 0}$} \label{step:reducD:begin}
        \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
        \STATE find $x_0$ such that $Dx_0=e$ \label{step:reducD:end}
        \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \label{step:reducD} \hfill {\color{olive} \# \Cref{reducD}}
      \ENDIF
      \IF{$A$ not in Smith Normal Form} \label{step:solsLP:begin}
        \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
        \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$ \label{step:solsLP:end}
        \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill \color{olive} \# \Cref{solsLP} \label{step:solsLP}
      \ENDIF
      \STATE $r \leftarrow \text{rank}(A)$ \label{step:core:begin}
      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$} 
        \IF{$\bigvee_{i=r+1}^n c_i \neq 0$}
        \RETURN [UNBOUND, []] \hfill {\color{olive} \# \Cref{prop:reduc}, item \ref{prop:reduc_it2}}
        \ELSE
          %\STATE STATUS $\leftarrow$ FEAS
          \STATE $\lambda \leftarrow -\sum_{i=1}^r c_i b_i / s_i$
          \STATE $v \leftarrow \min_{1 \leq i \leq r} \val (c_i/s_i)$
          \IF{$\val \lambda < v$}
            \STATE choose $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
            \RETURN [FEAS, $y$] \hfill {\color{olive} \# \Cref{solutions}, item \ref{solutions:it1}}
          \ELSE
          \STATE $j \leftarrow \min_{1 \leq i \leq r} \{i : v = \val (c_i/s_i)\}$
          %find $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
          %and $\langle c,y\rangle = \pi^v\OK$
            \RETURN [FEAS, ${\bf e}_j$] \hfill {\color{olive} \# \Cref{solutions}, item \ref{solutions:it2}}
          \ENDIF
        \ENDIF 
      \ENDIF 
        %\STATE
        %\STATE
        %\RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
      %\ENDIF \label{step:core:end}
      \RETURN [INFEAS, []] \label{step:core:end}
    \end{algorithmic}
\end{algorithm}

@@

  The core of \Cref{algo_LP} is on steps \ref{step:core:begin}-\ref{step:core:end}.

  TO BE CONTINUED.
\end{proof}

\begin{remark}
  If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that
  $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th
  which is $1$.
\end{remark}

>>>>

\begin{algorithm}
    \caption{\textbf{SOLVELPval}($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
        \RETURN [INFEAS, []] \label{step:linear_empty}
      \ENDIF
      \IF{$D \neq {\bf 0}$} \label{step:reducD:begin}
        \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
        \STATE find $x_0$ such that $Dx_0=e$ \label{step:reducD:end}
        \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \label{step:reducD} \hfill {\color{olive} \# \Cref{reducD}}
      \ENDIF
      \IF{$A$ not in Smith Normal Form} \label{step:solsLP:begin}
        \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
        \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$ \label{step:solsLP:end}
        \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill \color{olive} \# \Cref{solsLP} \label{step:solsLP}
      \ENDIF
      \STATE $r \leftarrow \text{rank}(A)$ \label{step:core:begin}
      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$} \label{step:condition}
        \IF{$\bigvee_{i=r+1}^n c_i \neq 0$}
        \RETURN [UNBOUND, []] \hfill {\color{olive} \# \Cref{prop:reduc}, item \ref{prop:reduc_it2}} \label{step:unbound}
        \ELSE
          %\STATE STATUS $\leftarrow$ FEAS
          \STATE $\lambda \leftarrow -\sum_{i=1}^r c_i b_i / s_i$
          \STATE $v \leftarrow \min_{1 \leq i \leq r} \val (c_i/s_i)$
          \IF{$\val \lambda < v$}
            \STATE choose $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
            \RETURN [FEAS, $y$] \hfill {\color{olive} \# \Cref{solutions}, item \ref{solutions:it1}}
          \ELSE
          \STATE $j \leftarrow \min_{1 \leq i \leq r} \{i : v = \val (c_i/s_i)\}$
          %find $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
          %and $\langle c,y\rangle = \pi^v\OK$
            \RETURN [FEAS, ${\bf e}_j$] \hfill {\color{olive} \# \Cref{solutions}, item \ref{solutions:it2}}
          \ENDIF
        \ENDIF 
      \ENDIF 
        %\STATE
        %\STATE
        %\RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
      %\ENDIF \label{step:core:end}
      \RETURN [INFEAS, []] \label{step:core:end}
    \end{algorithmic}
\end{algorithm}

@@

  The core of \Cref{algo_LP} is on steps \ref{step:core:begin}-\ref{step:core:end}.
  If $\val(b_i) \geq 0$, for all $i=1,\ldots,r+1$, with $r = \mathrm{rank}(A)$,
  by \Cref{prop:reduc}, item \ref{prop:reduc_it1}, the problem \eqref{LP} is feasible.
  Two cases can occur under this assumption:
  either at least one of the $n-r$ last coefficients of $c'$ is non-zero,
  in which case,
  by \Cref{prop:reduc}, item \ref{prop:reduc_it2}, the problem is
  unbounded and has no solution, thus the output on step \ref{step:unbound} is correct;
  or all the $n-r$ last coefficients of $c'$ are null. In this case the solutions
  are explicitely constructed according to \Cref{solutions}.

  If the condition on step \ref{step:condition} is not satisfied, the problem
  is infeasible by \Cref{prop:reduc} (step \ref{step:core:end}).
\end{proof}

%\begin{remark}
%  If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that
%  $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
%  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th
%  which is $1$.
%\end{remark}
